Unified Understanding of the Dielectric Nature of Two-Dimensional Materials

### 2018-10-16 paper.tex
Change section 1 of main text

The central place of dielectric properties, especially the static
dielectric constant in material research
\cite{Dressel_2001_electrodynamics} drives the pursuit for a unified
model between the electronic and dielectric properties of materials.
In fact, some pioneering work\cite{Moss_1950_relation} discovered
relationships between the dielectric constant $\varepsilon$ and other
physical properties, in particular the band gap $E_{\mathrm{g}}$
(minimal optical transition energy) of bulk
semiconductors. Moss\cite{Moss_1950_relation,Moss_1985_n_Eg} showed
that $E_{\mathrm{g}}$ and $\varepsilon$ follow a semi-empirical
relationship, known as the Moss relation:
\begin{equation}
\label{eq:Moss-relations}
\varepsilon^{2} E_{\mathrm{g}} \approx 95\ \mathrm{eV}
\end{equation}
Other similar semi-empirical models for the relationship between
$\varepsilon$ and $E_{\mathrm{g}}$ of bulk semiconductors have also
been proposed
\cite{Ravindra_1979_eps_Eg,Ravindra_1980_model,Ravindra_2007_Eg_rev}. Despite
the minor difference between the formulae used, it is clear that the
there exists certain general electronic relations in bulk
semiconductors. The existence of such general relationship is also of
high practical importance: it is generally more straightforward and
accurate to measure the band gap $E_{\mathrm{g}}$ than the static
dielectric constant $\varepsilon$, as the latter is strongly dependent
on dependent on several critical details on the sample measurements,
such as contamination, disorder, and model interpretation. With the
Moss relationship or other similar models, it is feasible to predict
the dielectric constant of a bulk semiconductor with a reasonable
degree of certainty.

While the relation between the electronic and dielectric properties
for bulk semiconductors are well-established, it is unknown if such
relation still exists in low-dimensional materials. For instance,
two-dimensional (2D) materials, the atomically-thin crystalline layers
\cite{Novoselov_2016}, are known to have distinct electronic
\cite{Mak_2010,Tran_2014} and dielectric properties
\cite{Keldysh_1979_eps_multi,Sharma_1985} compared with their bulk
counterparts, making the empirical relations of dielectric constant in
bulk materials, like the Moss relation invalid within the context of
2D materials. More critically, the static dielectric constant, a
quantity associated with the macroscopic dielectric property and
commonly obtained by theoretical calculations of 2D materials
\cite{Ramasubramaniam_2012,Wang_2016_Aip,Laturia_2018}, may not well
describe the microscopic and anisotropic dielectric nature of 2D
materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Therefore, an
accurate description of the 2D dielectric nature is the prerequisite
for the 2D Moss-like relations. Here we show that instead of the
dielectric constant $\varepsilon$, the 2D polarizabilty $\alpha$
correctly captures the dielectric nature of a 2D material for both
in-plane and out-of-plane polarizations. Based on first principles
simulation of over 50 kinds of monolayer 2D materials, we reveal the
long-sought universal dielectric scale relation in the 2D world: the
in-plane polarizability $\alpha^{\parallel}$ is inversely proportional
to the minimal bandgap $E_{\mathrm{g}}$, while the out-of-plane
polarizability $\alpha^{\perp}$ is closely related with the intrinsic
thickness of 2D materials. The anisotropy of the 2D polarizability is
further explained by a confined quantum model. The universal relations
provide quantitative prediction of the dielectric properties of 2D
materials, which leads to better design and understanding of
electronic devices based on 2D materials and their heterostructures
. Furthermore, such relations bridge the gap between the 2D and 3D
properties, and ultimately pushes the boundary of the understanding of
electronic screening in both dimensions.

@@

To get the correct description between the dielectric properties of a
2D material with other physical quantities, an accurate description of
the dielectric nature must first be established. As shown in Figure
\ref{fig-1}a, in first principles calculations, an isolated 2D
material needs to be placed in a periodically repeating superlattice
(SL) with a certain length $L$ in the out-of-plane direction to
prevent the interaction from periodic images. The macroscopic
dielectric constant from the superlattice, is the combined effect of
the intrinsic 2D dielectric properties and the vacuum spacing inside
the superlattice. From the classical electrostatics, we know that the
dielectric tensor $\varepsilon_{\alpha \beta}$, is determined by the
response of dipole density $\mathbf{P}_{\alpha}$ under small
perturbative external field $\mathbf{E}_{\beta}$, such that:
\begin{equation}
  \label{eq:def-eps}
  \begin{aligned}
    \varepsilon_{\alpha \beta} &= \kappa_{\alpha \beta} +
    \frac{\partial \mathbf{P}_{\alpha}}{\varepsilon_{0} \partial \mathbf{E}_{\beta}} \\
    &= \kappa_{\alpha \beta} + {\displaystyle \frac{\partial {\displaystyle
          \int_{\mathrm{SL}} \rho(\mathbf{r})\mathbf{r}_{\alpha} d^{3}\mathbf{r}}}{\Omega \varepsilon_{0} \partial \mathbf{E}_{\beta}}}
  \end{aligned}
\end{equation}
where $\alpha$, $\beta$ are the directions in $(x, y, z)$,
$\kappa_{\alpha\beta}$ is the dielectric tensor of the environment
(equals 1 if the environment is vacuum), $\rho$ is the spatial charge
density, $\Omega$ is the volume of the superlattice and
$\varepsilon_{0}$ is vacuum permittivity. For 2D semiconductors, the
off-diagonal elements of the dielectric tensor ($\alpha \neq \beta$)
is always 0. Therefore we can distinguish two components of the
SL dielectric constant, namely the in-plane

@@

($\varepsilon_{\mathrm{SL}}^{\perp}$) dielectric constant, where

@@

$\varepsilon_{\mathrm{SL}}^{\perp} =
\varepsilon_{\mathrm{SL}}^{zz}$. Consider the volume $\Omega=AL$,
where $A$ is the area of SL in the xy-plane, and $\kappa \equiv 1$, we
see that both $\varepsilon^{\parallel}_{\mathrm{SL}}$ and
$\varepsilon^{\perp}_{\mathrm{SL}}$ depends on the superlattice length
$L$. On the other hand, the induced dipole of the 2D to an external
field is localized within a confined region near the 2D plane. We show
this by plot the charge density change
$\Delta \rho=\rho(\mathbf{E}) - \rho(\mathbf{E}=0)$ along the z-axis
for an isolated 2H-MoS$_{2}$ layer under
$|\mathbf{E}|=0.01 \mathrm{V\cdot \AA}^{-1}$, as illustrated in Figure
\ref{fig-1}b. The induced dipole only extends to ~12 \AA{} in the
z-direction. Combining the two effects discussed above, it is
erroneous to use directly use the value $\varepsilon_{\mathrm{SL}}$
to present the dielectric nature of a 2D material. We need to find the
$L$-independent quantity to present the intrinsic dielectric
properties of the 2D material. By multiplying $\mathbf{P}$ with $L$,
we get the sheet polarization density $\mathbf{\mu}$, such that
$\mathbf{\mu}=\int_{\mathrm{SL}} \rho(\mathbf{r})rd^{3} \mathbf{r}/A$,

@@

molecular polarizability, the sheet polarization density
$\mathbf{\mu}$ is associated with the 2D polarizability $\alpha$ by:
$\mathbf{\mu} = \alpha \mathbf{E}_{\mathrm{loc}}$, where

@@

screening yields $\mathbf{E}_{\mathrm{loc}}=\mathbf{E}+\mathbf{\mu}/L$

@@

Eq. \ref{eq:def-eps}, we get the expressions for the in-plane and
out-of-plane 2D polarizabilities, $\alpha^{\parallel}$ and
$\alpha^{\perp}$, respectively:

@@

  \alpha^{\parallel} &= \varepsilon_{0}(\varepsilon_{\mathrm{SL}}^{\parallel} - 1)L\\

@@

    \alpha^{\perp} &= \varepsilon_{0}\left(1 - \frac{1}{\varepsilon_{\mathrm{SL}}^{\parallel}}\right)L

@@

The $L$-dependence presented in $\varepsilon$ is then removed in the
2D polarizabilities.  We note that although both scaling relations
have been proposed in individual studies
\cite{Cudazzo_2011_screening_2D,Kumar_2016_jpcc,Kumar_2016_PRB}, the
work presented here is the first attempt of unifying the dielectric
properties of 2D materials by both the in- and out-of-plane
polarizabilities, which provides a universal description of dielectric
nature from strict 2D system to the  3D world. Next we examine
how good the 2D polarizability can present its dielectric
nature. Figure \ref{fig-1}c and \ref{fig-1}d show the

@@

$\varepsilon_{\mathrm{SL}}^{\perp}$ as functions of $L$ of a
2H-MoS$_{2}$ monolayer. As expected the $\varepsilon_{\mathrm{SL}}$
decreases with $L$ in both cases and does not converge even when the
SL size is as large as 60 \AA{}. On the contrary, the
$\alpha^{\parallel}$ and $\alpha^{\perp}$ calculated using
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}, remain
almost constant when $L>$15 \AA{}. We have further examined the
$\alpha-L$ relation for other group 6 transitional metal
dichalcogenides (TMDCs), including 2H-MoSe$_{2}$, 2H-MoTe$_{2}$,
2H-WS$_{2}$, 2H-WSe$_{2}$, 2H-WTe$_{2}$ (details see Supplementary
Section XX \todo{TBD}). All materials exhibit constant $\alpha$ for
$L>$15 \AA{}, confirming that $\alpha$ is the true descriptor for the
dielectric nature of 2D materials. The calculation of $\alpha$ from
first principles dielectric response does not require the \textit{a
  priori} determination of the thickness of the 2D material, a
quantity which is not well defined. On the other hand, the widely-used
method of treating the 2D material as a dielectric slab with thickness
$\delta$ and uniform dielectric constant $\varepsilon_{\mathrm{2D}}$
\cite{Sharma_1985,Cudazzo_2011_screening_2D,Trolle_2017_eps_subst},
tends to give nonphysical pictures of the 2D dielectric properties due
to the ambiguity of $\delta$ (details see Supplementary Section XX
\todo{TBD}). In the following sections, we will pursue the universal
description for the dielectric nature of 2D materials starting from
the 2D polarizability.

@@

All results calculated for this paper were the result of \emph{ab
  initio} simulations carried out using plane-wave Density Functional
Theory (DFT) package VASP
\cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2} using the Projector
Augmented Wave (PAW) approach with Kresse’s mainly GW
Pseudopotentials \cite{Kresse_1999_pseudopotentials}. Band gaps were
calculated using the Heyd-Scuseria-Ernzerhof hybrid functional (HSE06)
\cite{Heyd_2003,HSE_2006}, with Spin Orbit Coupling (SOC) explicitly
included. The geometries were converged both in cell parameters and
ionic positions, with forces below 0.04 eV/\AA. To ensure the accuracy
of dielectric property of monolayer, a vacuum spacing of $>$ 15 \AA is
used. A k-point grid of \(7\times7\times1\) was used to relax the
superlattice, with an initial relaxation carried out at the
Perdew-Burke-Ernzerhof
(PBE)\cite{Perdew_1996,Ernzerhof_1999,Paier_2005_PBE}
exchange-correlation functional level and a subsequent relaxation
carried out at HSE06 level, allowing both cell parameters and ionic
positions to relax each time. In VASP, the tag PREC=High was used,
giving a plane wave kinetic energy cutoff of 30\% greater than the
highest given in the pseudopotentials used in each material,
guaranteeing that absolute energies were converged to a few meV and
the stress tensor to within a few kBar.  Calculation of the
macroscopic ion-clamped dielectric tensor were carried out with an
18$\times$18$\times$1 k-grid and electric field strength of 0.001
eV/\AA. Bulk layered materials were constructed by relaxing the c-axis
length of corresponding monolayer material with the interlayer van der
Waals (vdW) interactions calculated by non-local vdW correlation
functional\cite{Lee_2010_vdFD2}. The dielectric properties of bulk
layered materials were calculated at PBE level with
18$\times$18$\time$6 k-grid with same parameter as for monolayer.

>>>>

The central place of dielectric properties, especially the static
dielectric constant in material research
\cite{Dressel_2001_electrodynamics} drives the pursuit for a unified
model between the electronic and dielectric properties of materials.
In fact, some pioneering work\cite{Moss_1950_relation} discovered
relationships between the dielectric constant $\varepsilon$ and other
physical properties, in particular the band gap $E_{\mathrm{g}}$
(minimal optical transition energy) of bulk
semiconductors. Moss\cite{Moss_1950_relation,Moss_1985_n_Eg} showed
that $E_{\mathrm{g}}$ and $\varepsilon$ follow a semi-empirical
relationship, known as the Moss relation:
\begin{equation}
\label{eq:Moss-relations}
\varepsilon^{2} E_{\mathrm{g}} \approx 95\ \mathrm{eV}
\end{equation}
Other similar semi-empirical models for the relationship between
$\varepsilon$ and $E_{\mathrm{g}}$ of bulk semiconductors have also
been proposed
\cite{Ravindra_1979_eps_Eg,Ravindra_1980_model,Ravindra_2007_Eg_rev}. Despite
the minor difference between the formulae used, it is clear that there
exists certain general electronic relations in bulk
semiconductors. The existence of such general relationship is also of
high practical importance: it is generally more straightforward and
accurate to measure the band gap $E_{\mathrm{g}}$ than the static
dielectric constant $\varepsilon$, as the latter is strongly dependent
on several critical details on the sample measurements, such as
contamination, disorder, and model interpretation. With the Moss
relationship or other similar models, it is feasible to predict the
dielectric constant of a bulk semiconductor with a reasonable degree
of certainty.

While the relation between the electronic and dielectric properties
for bulk semiconductors are well-established, it is unknown if such
relation still exists in low-dimensional materials. For instance,
two-dimensional (2D) materials, the atomically-thin crystalline layers
\cite{Novoselov_2016}, are known to have distinct electronic
\cite{Mak_2010,Tran_2014} and dielectric properties
\cite{Keldysh_1979_eps_multi,Sharma_1985} compared with their bulk
counterparts, making the empirical relations of dielectric constant in
bulk materials, like the Moss relation invalid within the context of
2D materials. More critically, the static dielectric constant, a
quantity associated with the macroscopic dielectric property and
commonly obtained by theoretical calculations of 2D materials
\cite{Ramasubramaniam_2012,Wang_2016_Aip,Laturia_2018}, may not well
describe the microscopic and anisotropic dielectric nature of 2D
materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Therefore, an
accurate description of the 2D dielectric nature is the prerequisite
for a 2D Moss-like relation. Here we show that instead of the
dielectric constant $\varepsilon$, the 2D polarizabilty $\alpha$
correctly captures the dielectric nature of a 2D material for both
in-plane and out-of-plane polarizations. Based on first principles
simulation of over 50 kinds \todo{some more?} of monolayer 2D
materials, we reveal the long-sought universal dielectric scale
relation in the 2D world: the in-plane polarizability
$\alpha^{\parallel}$ is inversely proportional to the minimal bandgap
$E_{\mathrm{g}}$, while the out-of-plane polarizability
$\alpha^{\perp}$ is closely related with the intrinsic thickness of 2D
materials. The anisotropy of the 2D polarizability is further
explained by a confined quantum model. The universal relations provide
quantitative prediction of the dielectric properties of 2D materials,
which leads to better design and understanding of electronic devices
based on 2D materials and their heterostructures. Furthermore, such
relations bridge the dielectric properties between the 2D materials
and their 3D counterparts, and ultimately pushes the boundary of the
understanding of electronic screening in both dimensions.

@@

In persuit of the Moss-like relation of 2D materials, a accurate
description of the dielectric properties of 2D materials needs to be
established. One known issue is that the concept of macroscopic
dielectric constant is ill-defined for 2D materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D,Nazarov_2015_2D_3D}. As
shown in Figure \ref{fig-1}a \todo{I'll change upon your change of Fig
  1a}, in first principles calculations, an isolated 2D material is
placed at the xy-plane of a periodically repeating superlattice (SL)
with a length $L$ along the z-direction large enough to prevent the
interactions between periodic images. The macroscopic dielectric
tensor from the superlattice $\varepsilon_{\mathrm{SL}}$, from
fundamental electrostatics, is determined by the response of
volumetric dipole density $\boldsymbol{P}^{p}$, under small perturbative
external field $\boldsymbol{E}^{q}$, where $p$, $q$ are the
directions in $(x, y, z)$,such that:
\begin{subequations}
      \label{eq:def-eps-1}
    &\varepsilon^{p} &= \kappa^{pq} +
                                 {\displaystyle \frac{\partial \boldsymbol{P}^{p}}
                                 {\varepsilon_{0} \partial \boldsymbol{E}^{q}}} \\
          \label{eq:def-eps-2}
    &\boldsymbol{P}^{p} &=  {\displaystyle \frac{\boldsymbol{u}^{p}}{\Omega}}
                          = {\displaystyle \frac{{\displaystyle
          \int_{\mathrm{SL}} \rho(\boldsymbol{r}) \boldsymbol{r}^{p} d^{3}\boldsymbol{r}}}
                          {AL}}
\end{subequations}
$\kappa$ is the dielectric tensor of the environment, $\boldsymbol{u}$
is the total dipole moments of the SL, $\rho$ is the spatial charge
density, $\Omega=AL$ is the volume of the SL, $A$ is the xy-plane area
of the SL and $\varepsilon_{0}$ is vacuum permittivity. For the
majority of 2D semiconductors, the off-diagonal elements of the
dielectric tensor ($p \neq q$) tend to be negligible.  Consider that
the 2D material is placed in vacuum, such that $\kappa^{pp} \equiv 1$
and $\kappa^{pq} \equiv 0$, we can distinguish two components of the
SL dielectric tensor, namely the in-plane

@@

($\varepsilon_{\mathrm{SL}}^{\perp}$) dielectric constants, where

@@

$\varepsilon_{\mathrm{SL}}^{\perp} = \varepsilon_{\mathrm{SL}}^{zz}$
\todo{geometry or numerical average?}. Due to the absence of bonding
along the z-direction, the induced charge density of a 2D material is
highly confined. Figure \ref{fig-1}a demonstrates the charge density
difference between zero and finite electric fields,
$\Delta \rho=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ along the
z-axis for an isolated 2H-MoS$_{2}$ layer under
$|\boldsymbol{E}_{z}|=0.01 \mathrm{V\cdot \AA}^{-1}$, which only
extends to ~12 \AA{} along the z-direction inside the SL. When $L$ is
large enough that the induced dipoles from periodic images do not
overlap, the total dipole moments $\boldsymbol{u}$ of the SL in
Eq. \ref{eq:def-eps-2} is independent of $L$. As a consequence, we can
see from Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, that both
$\varepsilon^{\parallel}_{\mathrm{SL}}$ and
$\varepsilon^{\perp}_{\mathrm{SL}}$ depend on the SL length $L$. We
show this by plotting $\epsilon^{\parallel}_{\mathrm{SL}}$ and
$\epsilon^{\perp}_{\mathrm{SL}}$ as functions of $L$ for 2H-type group
6 transitional metal dichalcogenides (TMDCs, 2H-MX$_{2}$, where M=Mo,
W and X=S, Se, Te), in the top panels of Figure \ref{fig-1}b and
\ref{fig-1}c \todo{change order!}, respectively. We can also observe
that neither $\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
$\varepsilon^{\perp}_{\mathrm{SL}}$ converges with the superlattice
length $L$ due to fact that the long-range Coulomb interaction could
not be completed screened, which is computationally unpractical
\cite{Hueser_2013_2Dvs3D}. The $L$-dependency of macroscopic
dielectric constant makes it erroneous to use
$\varepsilon_{\mathrm{SL}}$ to present the dielectric nature of a 2D
material. Therefore, we need to find a $L$-independent quantity to
present the intrinsic dielectric properties of the 2D materials. As
discussed previous, since the total dipole moments $\mathbf{u}$ remain
constant with $L$, we can define the surface or sheet polarization
density matrix $\boldsymbol{\mu}$, by multiplying
Eq. \ref{eq:def-eps-2} with $L$, that
$\boldsymbol{\mu}^{p} = \boldsymbol{P}_{p}L = \int_{\mathrm{SL}}
\rho(\boldsymbol{r}) \boldsymbol{r}_{p}d^{3} \boldsymbol{r}/A$,

@@

molecular polarizability \cite{Israelachvili_2011}, the sheet
polarization density $\boldsymbol{\mu}$ is associated with the 2D
polarizability tensor $\alpha$ through:
$\boldsymbol{\mu}^{p} = \sum_{q} \alpha^{pq}
\mathbf{E}_{\mathrm{loc}}^{q}$ \cite{T_bik_2004}, where

@@

screening yields
$\boldsymbol{E}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}^{\perp}/L$

@@

Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, we derive the
expressions for the in-plane and out-of-plane 2D polarizabilities,
$\alpha^{\parallel}$ and $\alpha^{\perp}$, respectively:

@@

  &\alpha^{\parallel} &= \varepsilon_{0}(\varepsilon_{\mathrm{SL}}^{\parallel} - 1)L\\

@@

    &\alpha^{\perp} &= \varepsilon_{0}\left(1 - {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}}\right)L

@@

The bottom panels of Figure \ref{fig-1}b and \ref{fig-1}c show the
$\alpha^{\parallel}$ and $\alpha^{\perp}$ of the TMDCs as functions of
$L$, calculated using Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}. We observe that both $\alpha^{\parallel}$ and
$\alpha^{\perp}$ remain almost constant when $L>$15 \AA{}. In
addition, by varying the value of $\alpha^{\parallel}$ and
$\alpha^{\perp}$, we can nicely reproduce the $L$-dependence of

@@

$\varepsilon_{\mathrm{SL}}^{\perp}$, respectively (Figure \ref{fig-1}b
and \ref{fig-1}c insets). These findings indicate that the 2D
polarizability, instead of the dielectric constant, is the true
descriptor of the dielectric properties of 2D materials.

We note that the dielectric properties of 2D materials are also often
modeled using an effect medium approach, which treats the 2D material
as a slab with effective permittivity $\varepsilon_{\mathrm{2D}}$ and
thickness $\delta$
\cite{Sharma_1985,Cudazzo_2011_screening_2D,Matthes_2016,Trolle_2017_eps_subst,Laturia_2018}. Such
methods require \textit{a priori} determination of $\delta$, a
quantity with controversial definitions \cite{Mas_Ballest__2011}. In
such approaches, $\varepsilon_{\mathrm{2D}}$ and $\delta$ have to be
determined by fitting the $L$-dependent data of
$\varepsilon_{\mathrm{SL}}$, which is not only computational
expensive, but also fails to capture the anisotropy of the 2D
dielectric properties (details see Supplementary Section S1). On the
other hand, calculating 2D polarizabilities requires no knowledge of
$\delta$ (see Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}), and correctly presents the anisotropy of 2D
dielectric nature that $\alpha^{\parallel} > \alpha^{\perp}$.  With
the polarizability as the true descriptor of 2D dielectric properties,
we will reveal the universal Moss-like relation of 2D materials.

@@

All results calculated for this paper were the result of \emph{ab
  initio} simulations carried out using plane-wave Density Functional
Theory (DFT) package VASP
\cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2} using the Projector
Augmented Wave (PAW) approach with Kresse’s mainly GW
Pseudopotentials \cite{Kresse_1999_pseudopotentials}. Band gaps were
calculated using the Heyd-Scuseria-Ernzerhof hybrid functional (HSE06)
\cite{Heyd_2003,HSE_2006}, with Spin Orbit Coupling (SOC) explicitly
included. The geometries were converged both in cell parameters and
ionic positions, with forces below 0.04 eV/\AA. To ensure the accuracy
of dielectric property of monolayer, a vacuum spacing of $>$ 15 \AA is
used. A k-point grid of \(7\times7\times1\) was used to relax the
superlattice, with an initial relaxation carried out at the
Perdew-Burke-Ernzerhof
(PBE)\cite{Perdew_1996,Ernzerhof_1999,Paier_2005_PBE}
exchange-correlation functional level and a subsequent relaxation
carried out at HSE06 level, allowing both cell parameters and ionic
positions to relax each time. In VASP, the tag PREC=High was used,
giving a plane wave kinetic energy cutoff of 30\% greater than the
highest given in the pseudopotentials used in each material,
guaranteeing that absolute energies were converged to a few meV and
the stress tensor to within a few kBar.  Calculation of the
macroscopic ion-clamped dielectric tensor were carried out with an
18$\times$18$\times$1 k-grid and electric field strength of 0.001
eV/\AA. Bulk layered materials were constructed by relaxing the c-axis
length of corresponding monolayer material with the interlayer van der
Waals (vdW) interactions calculated by non-local vdW correlation
functional\cite{Lee_2010_vdFD2}. The dielectric properties of bulk
layered materials were calculated at PBE level with
18$\times$18$\times$6 k-grid with same parameter as for monolayer.
